\LARGE \bf Grasp Metric for Gaussian Proccess Implicit Surface Representation of Shape Uncertainity

### 2014-07-04 paper.tex
Added bib and started Lipschitz section

@@

\begin{equation}
p(c_i = \gamma{g}, n_i = k) = p(n_i = k | h(\gamma{g}))*p(c_i = \gamma{g})
\end{equation}

@@

\begin{equation}
P(n_i = k) = \int_T  p(n_i = k | h(\gamma{g}))*p(c_i = \gamma{g}) dg
\end{equation}

@@

\begin{equation}
P(n_i = k) = \sum_T  p(n_i = k | h(\gamma{g}))*p(c_i = \gamma{g}) dg
\end{equation}

@@

\subsection{Other Thoughs Not Finished}
The derivation above assumes that the robot doesn't have any noise in its movements. To accomdate noise in the position of the gripper at time $t$, $x_t$ given control input $u_{t}$ and previous states $x_{1:t-1}$, we introduce the following probability $P(x_t=k|u_t,x_{1:t-1})$. This can be computed by methods like an Extended Kalman Filter (EKF) or a particle filter. For simplicity we assume that it is a Guassian distribution.

@@

>>>>

\newtheorem{theorem}{Theorem}

@@

\begin{equation}
p(c_i = \gamma(g), n_i = k) = p(n_i = k | h(\gamma(g)))*p(c_i = \gamma(g))
\end{equation}

@@

\begin{equation}
P(n_i = k) = \int_T  p(n_i = k | h(\gamma(g)))*p(c_i = \gamma(g)) dg
\end{equation}

@@

\begin{equation}
P(n_i = k) = \sum_T  p(n_i = k | h(\gamma(g)))*p(c_i = \gamma(g)) dg
\end{equation}

@@

\subsection{Other Thoughts (Not Finished)}
The derivation above assumes that the robot doesn't have any noise in its movements. To accommodate noise in the position of the gripper at time $t$, $x_t$ given control input $u_{t}$ and previous states $x_{1:t-1}$, we introduce the following probability $P(x_t=k|u_t,x_{1:t-1})$. This can be computed by methods like an Extended Kalman Filter (EKF) or a particle filter. For simplicity we assume that it is a Gaussian distribution.

@@

Following recent work on proving a Lipschitz bound on the Ferrari-Canny Metric \cite{pokorny2013classical}, we prove that an extension is possible to give a probabilistic bound on the change in grasp quality. We rewrite the results here:

\subsection{Prior Work}

We use the following notation $Q(g)$ refers to the exact $L^1$ grasp quality. It is denoted by the following

\begin{align}
Q(g) &= \mbox{max}(0,q(g)) = -d(0,\mbox{Conv}(0 \cup S(g))\\
-d(0,S) &= min_{||z|| = 1} h_{S(z)}\\
h_{S(z)} &= \mbox{sup}_{s\in S}<s,z>\\
\end{align}

We denote the Ferrari-Canny version, which approximates the friction cone by a linearized set of wrenches\cite{ferrari1992}, as $Q^-_l(g)$.\\

\begin{theorem}
For any grasp g, we have $0 \leq Q_l^-(g) \leq Q(g)$. Furthermore, $||Q(g) - Q^-_l(g)|| \rightarrow 0$ as $l \rightarrow \infty$ when $Q_l^-(g)$ is computed using a uniform approximation of the friction cones with $l$ edges. \\
\end{theorem}

\begin{theorem}
We have \\

\begin{align}
q(g) = \min_{u\in \mathbb{R}^6, ||u|| =1} h_{S(g)}(u) = \min_{u\in \mathbb{R}^6, ||u|| =1} \max_{i=1,...,m} h_{W_i(g)}(u),\\
\end{align}

where $h_{S(g)}$ is convex on $\mathbb{R}^6$. Observe that q is invariant under fixed translation of the grasp center and contact positions. Furthermore, let $\mathbb{B}(r) = \lbrace x \in \mathbb{R}^3 : ||x|| \leq r \rbrace$. Then q is Lipschitz continuous on grasps with $m$ contact points lying in the set $X = \lbrace (c_1,...,c_m,n_1,...,n_m,z) : (c_i-z) \in \mathbb{B}(r), n_i \in \mathbb{S}^2 \rbrace$ with a Lipschitz constant given by $L= (1+\mu)(1+r)$ and where the chose distance measure \\

$d(g,g') = \sum_i ||(c_i-z)-(c_i'-z')|| + \sum_i ||n_i - n_i'||$\\

We hence have \\

$|q(g) - q(g')| \leq Ld(g,g')$ for all $g,g' \in X$. \\

Since $Q(g) = max(0,q(g))$, Q is also Lipschitz continuous with the same constant L on X. 
\end{theorem}

\subsection{Our Extension}
From our distributions $p(c_i=\gamma(t))$ and $p(n_i = x)$, we can denote the variance on the following terms as $\sigma_{c_i}$ and $\Sigma_{n_i}$. Thus,
